Combining of local and global search in the parallel nested optimization scheme \thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2019-12-02 2020/PAVT_Nested_Full/pavt_paper.tex
Include two more references

In the present paper, the global optimization problems and the numerical methods of solving these 
ones are considered. 
Regarding the character of the dependence of the objective function on its parameters, an assumption 
is made that it is multiextremal with respect to selected variables only, and the dependence on the rest 
ones has a local character. 
The problems of this type may arise in the identification of the unknown parameters of the 
mathematical models on the base of the results of experiments. 
A parallel computational scheme, which accounts for this feature has been proposed.
The novel scheme is based on the idea of the nested (recursive) optimization when at the upper 
recursion level the optimization with respect to the globally-meaning variables is performed (using 
the global optimization method), and at the lower one the local optimization problems are solved (using 
the local method). The generated local subproblems will not affect each other, and the solving of these 
ones can be performed in parallel. The numerical experiments have been conducted on several 
hundred test problems confirming the efficiency of the proposed scheme of parallel computations.

@@

The global optimization problems arise often in various fields of modern science and technology. For 
example, the problems of finding the configurations of various chemical compounds corresponding to 
the minimum interaction energy are relevant \cite{Posypkin2014}. In particular,  such problems arise 
in the development of new medical drugs \cite{Sulimov}. The global optimization problems arise in 
many other applications as well (see the review \cite{Pinter2006}).

>>>>

In the present paper, the global optimization problems and the numerical methods of solving these 
ones are considered. 
Regarding the character of the dependence of the objective function on its parameters, an assumption 
is made that it is multiextremal with respect to selected variables only, and the dependence on the rest 
ones has a local character. 
The problems of this type may arise in the identification of the unknown parameters of the 
mathematical models on the base of the results of experiments. 
A parallel computational scheme, which accounts for this feature has been proposed.
The novel scheme is based on the idea of the nested (recursive) optimization when at the upper 
recursion level the optimization with respect to the globally-meaning variables is performed (using 
the global optimization method), and at the lower one the local optimization problems are solved (using 
the local method). The generated local subproblems will not affect each other, and solving of these 
ones can be performed in parallel. The numerical experiments have been conducted on several 
hundred test problems confirming the efficiency of the proposed scheme of parallel computations.

@@

The global optimization problems arise often in various fields of modern science and technology. For 
example, the problems of finding the configurations of various chemical compounds corresponding to 
the minimum interaction energy are relevant \cite{Posypkin2014}. In particular,  such problems arise 
in the development of new medical drugs \cite{Sulimov}. 
Another example is the problem of finding optimal control parameters for complex processes \cite{Kalyulin2017,Modorskii2016}.
The global optimization problems arise in many other applications as well (see the review \cite{Pinter2006}).
